Box

### 2021-07-22 MS/box.Rmd
Box updated with Losia's comment

Here, $f(M_1) = \ln{M_1}$. By applying $f'(M_1) = 1/{M_1}$ (i.e. the first derivative of $lnM_1$ is $1/{M_1}$) to the delta method and using the variance's basic properties, we have:

@@

Note that the first term, $\frac{SD_{1}^2}{N_{1}}$ is once again the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as described by the Delta method. Readers may notice that this formula is now equivalent to the sampling variance for $ln_{RR}$ (Table 1). We can extend this sampling variance to include dependency between the groups as:

>>>>

Here, $f(M_1) = \ln{M_1}$. By applying $f'(M_1) = 1/{M_1}$ (i.e. the first derivative of $lnM_1$ is $1/{M_1}$) to the Delta method and using the variance's basic properties, we have:

@@

Note that the first term, $\frac{SD_{1}^2}{N_{1}}$ is once again the sampling variance for group 1, and we simply multiply this term by the square of the first derivative of $M_{1}$ as described by the Delta method. Readers may notice that this formula is now equivalent to the sampling variance for $lnRR$ (Table 1). We can extend this sampling variance to include dependency between the groups as:
